External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-12 CVPR2017_Review_Unified.tex
add

Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage. In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM. We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.

@@

The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment. Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.

The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes. The noisy images were collected under controlled indoor environment. Each scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments. To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments. Some samples are shown in Fig. \ref{fig3}. Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.

>>>>

Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.\ In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM.\ We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.

@@

The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment.\ Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.

The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes.\ The noisy images were collected under controlled indoor environment.\ Each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments.\ To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments. Some samples are shown in Fig.\ \ref{fig3}.\ Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
